Write title here

### 2021-07-13 manuscript/paper.tex
Fix stack of cylinders so that the initial configuration is same.

>>>>

\subsection{A rigid body on a boundary}

Consider a square rigid body on a surface, the density of the body is 800
kg$m^{-3}$, the simulation is in 2 dimensions. The side of the body is
$0.5$m. The stiffness in the normal direction is $10^5$N$m^{-1}$.

\textbf{The analysis corresponding to the current section is done in file
  code $rigidbodyonasurface.py$}
